---
title: "Statistical Tests"
output: html_document
date: '2022-06-10'
---
```{r}
#Importing the dataset after cleaning
library(readr)
dataset.mh <- read_csv("new_survey_dataset.csv")

```
# Data Visualization
```{r}
#Visualizing the ages of the workers
hist(dataset.mh$age, col="red",xlab = "Age", main = "Histogram Plot for ages", breaks = 15)
boxplot(dataset.mh$age, col="red")

```


```{r}
#Getting rid of the outliers
newDF<-subset(dataset.mh, 10 < age & age < 70)
hist(newDF$age, col="red",xlab = "Age" ,main = "Histogram Plot for ages",breaks = 15)
#Data transformating using log transformation
transformedDF<-transform(newDF, age.log=log2(age))
hist(transformedDF$age.log, col="blue",xlab = "Transformed age" ,main = "Histogram Plot for age",breaks = 15)
```

**We can assume that the data is not normally distributed**

# Confidence Interval for Mean

**A confidence interval is the mean of your estimate plus and minus the variation in that estimate.**

```{r}
#sd is known
norm.interval = function(data, variance, conf.level =0.95){
  z = qnorm((1 - conf.level)/2, lower.tail=FALSE)
  xbar = mean(data)
  sdx = sqrt(variance/length(data))
  c(xbar - z * sdx, xbar + z*sdx)
}

newDF.var <- var(newDF$age)
norm.interval(newDF$age, newDF.var)
```


```{r}
#Standard deviation is unknown
newDF.CI <- t.test(newDF$age)$conf.int
newDF.CI
```



# Single t-test
**Our aim here is to check whether the mean of the workers age is equal or less than 30 years old with a confidence level of 95%**
**H1: mu=<30, H1: mu>30, Alpha=0.05**


```{r}
#Applying Single t-test
t.test(newDF$age, mu=30, alt = "greater", conf = 0.95)
```
**Since the p-value is less than alpha, we reject the null hypothesis**

# Paired t-test
**Our aim is to compare the difference between the males and females**
**H1: mu=0, H1: mu!=0, Alpha=0.01**

```{r}
#Dividing the dataset to two groups
library("usethis")
library("devtools")
source_gist("https://gist.github.com/mrdwab/6424112")

sampledData<-stratified(newDF, "gender",select = list(gender= c("1","2")), size=200)

males.ages<-sampledData$age[1:200]
females.ages<-sampledData$age[201:400]

boxplot(males.ages, females.ages, col=c("blue","red"))

plot(males.ages, females.ages, col=c("blue", "red"), abline(a=0, b=1))
```

**We assume that the variables are metric and the difference of the paired values is normally distributed **

```{r}
t.test(males.ages, females.ages, mu=0, alt="two.sided", paired = T, conf = 0.99)
```
**Since the p-value is less than 0.05, we reject the null hypothesis**

# One Sample Z-Test

**A Z-test is a type of hypothesis test—a way for you to figure out if results from a test are valid or repeatable.**

# Z Test

- First visualize necessary column and convert to the normal distribution
```{r}
library(ggpubr)
library(moments)

#visualizing ages 
x= newDF$age
y = dnorm(x, mean(x), sd(x))

   
# Plot the graph.
plot(x, y, xlab = "age", ylab = "normilized ages")
```

- perform one sample z-test

```{r}
library(BSDA)
age_x <- sort(x)
mean(x)
z.test(age_x, mu=mean(age_x), sigma.x= sd(age_x))
```

- The test statistic for the one sample z-test is 0 and the corresponding p-value 1.

- Since p value is greater than .05, we have sufficient evidence to reject the null hypothesis.

